---
title: "ch-2_exercises&applied"
author: "wendy"
date: "April 4, 2016"
output: html_document
---

1. Describe the null hypotheses to which the p-values given in Table 3.4 correspond. Explain what conclusions you can draw based on these p-values. Your explanation should be phrased in terms of sales, TV, radio, and newspaper, rather than in terms of the coefficients of the linear model.

TV and radio are the significant predictor to the ads effect. 
Newspaper is not a significant predictor. 
--- refer to answers in the github, which is much better than mine. 

2. Carefully explain the differences between the KNN classifier and KNN regression methods.

both is to set a K and then get the result.
KNN regression is to calculate the parametric with the closest K data. 
KNN classifier is to get the result according to the higher percentage.

3. Suppose we have a data set with five predictors, X1 = GPA, X2 = IQ, X3 = Gender (1 for Female and 0 for Male), X4 = Interaction between GPA and IQ, and X5 = Interaction between GPA and Gender. The response is starting salary after graduation (in thousands of dollars). Suppose we use least squares to fit the model, and get βˆ0 = 50, βˆ1 = 2 0 , βˆ 2 = 0 . 0 7 , βˆ 3 = 3 5 , βˆ 4 = 0 . 0 1 , βˆ 5 =  -10

(a) Which answer is correct, and why? iv is correct
---> ans should be iii
i. For a fixed value of IQ and GPA, males earn more on average than females. 
ii. For a fixed value of IQ and GPA, females earn more on average than males. 
iii. For a fixed value of IQ and GPA,males earn more on average than females provided that the GPA is high enough.
iv. For a fixed value of IQ and GPA, females earn more on average than males provided that the GPA is high enough.

(b) Predict the salary of a female with IQ of 110 and a GPA of 4.0.
50 + 20*4 + .07*110 + 35*1 + .01*(110*4) - 10*(4*1)

(c) True or false: Since the coefficient for the GPA/IQ interaction term is very small, there is very little evidence of an interaction effect. Justify your answer.
evidence is to check the p value. P value could show if this effect is significant or not. 
coeffiecient is small is just their effect in the formular. 

4. 
a. the training RSS of the cubic regression would smaller than linear one, due to the overfitting
b. the test RSS of the cubic regression would higher than the linear one. 
c. the cubic regression's RSS should be smaller
d. hard to say depending on how the real relationship between X and Y

8. 
```
Auto.lm = lm(mpg~horsepower, data = Auto)
summary(Auto.lm)
predict(Auto.lm, data.frame(horsepower = c(98)), interval = "confidence")
predict(Auto.lm, data.frame(horsepower = c(98)), interval = "prediction")
```
i. yes, there is a relationship between the predictor and the response. 
ii. strong, the adjusted R-squared is .6049, t value is -24.5. 
iii. the relationship is negative
iv. ???? why different than the ans
result is 40-.15*98 = 25.3
95% confidence 40+(-.15+2*.006)*98 = 26.476
95% confidence 40+(-.15-2*.006)*98 = 24.124


```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```
